Target Markdown

### 2023-04-14 _targets.Rmd
engine

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)

@@

```{targets data_import}
list(

@@

```{targets matching_preparation}
list(

@@

```{targets topic_model}
list(

@@

```{targets network}

@@

```{targets RII1}

@@

```{targets RII2}

@@

```{targets RII3}

@@

```{targets RII4}

@@

```{targets RII4_2}

@@

```{targets final}

@@

    tar_target(full_indicator,
               calc_full_indicator(independent_topics),

>>>>

```{r, engine="targets", example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)

@@

```{r, engine="targets", data_import}
list(

@@

```{r, engine="targets", matching_preparation}
list(

@@

```{r, engine="targets", topic_model}
list(

@@

```{r, engine="targets", network}

@@

```{r, engine="targets", RII1}

@@

```{r, engine="targets", RII2}

@@

```{r, engine="targets", RII3}

@@

```{r, engine="targets", RII4}

@@

```{r, engine="targets", RII4_2}

@@

```{r, engine="targets", final}

@@

    tar_target(full_indicator,
               calc_full_indicator(independent_topics)
    )
               )
